Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-08 bckground.tex

It is interesting to note that most WMS developed to support LHC experiments are gradually evolving towards HPC resources, though none have reached sustained operational usage at the scales that PanDA has achieved for ATLAS on Titan.

>>>>

It is interesting to note that most WMS developed to support LHC experiments
are gradually evolving towards integrating HPC resources, though none have
reached sustained operational usage at the scales that PanDA has achieved for
ATLAS on Titan.

### 2017-07-08 conclusion.tex
Commented out AA919's text. I added the NGE contribution a few paragraphs before the end of Conclusion.

We characterized the experience by evaluating the efficiency, scalability and
reliability of both PanDA Broker and AthenaMP as deployed on Titan
(\S\ref{sec:panda_titan}). Our characterization highlighted the strengths and
limitations of the current design and implementation: PanDA Brokers enable the
sustained execution of millions of simulations per week but further work is
required to optimize its efficiency and reliability
(\S\ref{ssec:broker_titan}). PanDA Brokers support the concurrent execution of
multiple AthenaMP instances, enabling each AthenaMP to perform the concurrent
execution of up to 16 Geant4 simulators. Nonetheless, our characterization
showed how improving I/O performance could reduce overheads
(\S\ref{ssec:athenamp_titan}), increasing the overall utilization of Titan's
backfill availability. We introduced PanDA's next generation executor for HPC
systems, characterized its ability to support multi-generation workloads and
analyzed its scaling behavior. It enables the high-performance execution of
new workloads and advanced execution modes of traditional workloads.

@@

>>>>

We characterized the experience by evaluating the efficiency, scalability and
reliability of both PanDA Broker and AthenaMP as deployed on Titan
(\S\ref{sec:panda_titan}). Our characterization highlighted the strengths and
limitations of the current design and implementation: PanDA Brokers enable the
sustained execution of millions of simulations per week but further work is
required to optimize its efficiency and reliability
(\S\ref{ssec:broker_titan}). PanDA Brokers support the concurrent execution of
multiple AthenaMP instances, enabling each AthenaMP to perform the concurrent
execution of up to 16 Geant4 simulators. Nonetheless, our characterization
showed how improving I/O performance could reduce overheads
(\S\ref{ssec:athenamp_titan}), increasing the overall utilization of Titan's
backfill availability. We introduced PanDA's next generation executor for HPC
systems, characterized its ability to support multi-generation workloads and
analyzed its scaling behavior.  Performance tests on the next generation
executor demonstrate linear strong and weak scalability over several orders
of magnitude  of task and node counts.  Qualitatively, it enables the high-
performance execution of new workloads and advanced execution modes of
traditional workloads.

@@

% The development of NGE is looking forward to deal with these challenges by providing an abstraction layer for HPC resources together with a set of APIs for the coordination and fast deployment of heterogeneous workloads.  In this paper, we provided the results of a preliminary testing of the NGE. The testing pointed out the robustness of NGE at handling an high number of tasks and worker nodes by mantaining an overhead that grows linearly with the number of tasks.
